% !TEX encoding = UTF-8 Unicode

\begin{thebibliography}{x}
\addcontentsline{toc}{chapter}{\bibname}

\bibitem{webgl}
Parisi, Tony. WebGL: up and running. " O'Reilly Media, Inc.", 2012.

\bibitem{reviewoftrafficsim}
Kotusevski, G., and K. A. Hawick. "A review of traffic simulation software." (2009).

\bibitem{roadtrafficsim}
Road Traffic Simulation Software, hivatalos weboldal, \\
\url{https://www.anylogic.com/road-traffic/}, Internet, 2019.

\bibitem{SUMO}
Krajzewicz, Daniel, et al. "SUMO (Simulation of Urban MObility)-an open-source traffic simulation." Proceedings of the 4th middle East Symposium on Simulation and Modelling (MESM20002). 2002.
% \url{https://www.dlr.de/ts/en/desktopdefault.aspx/tabid-9883/16931_read-41000/}

\bibitem{anylogicpic}
Bobkowska, Katarzyna, et al. "GIS three-dimensional Modelling with geo-informatics techniques." Environmental Engineering. Proceedings of the International Conference on Environmental Engineering. ICEE. Vol. 10. Vilnius Gediminas Technical University, Department of Construction Economics \& Property, 2017.
% \url{https://www.researchgate.net/publication/316700661_GIS_three-dimensional_Modelling_with_geo-informatics_techniques}

\bibitem{heatmappic}
AnyLogic cloud, \\
\url{https://cloud.anylogic.com/model/6322b634-2cc5-4d40-90cf-3bb44c825ea7?mode=SETTINGS&tab=GENERAL},
Internet, 2019.

\bibitem{sumopic}
SUMO, Simulation of Urban MObility, hivatalos weboldal, \\
\url{https://sumo.dlr.de}, Internet, 2019.

\bibitem{geo}
Bereta, Konstantina, and Manolis Koubarakis. "Ontop of geospatial databases." International Semantic Web Conference. Springer, Cham, 2016.

\bibitem{mapsdoc}
Google Maps Platform Documentation,
\url{https://developers.google.com/maps/documentation/}, Internet 2019.

\bibitem{unity}
Goldstone, Will. Unity game development essentials. Packt Publishing Ltd, 2009.

\end{thebibliography}
